---
title: "Lab 03 - Nobel laureates"
author: "Benjamin Egan"
date: "Started on 1/27"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
nobel <- read_csv("data/nobel.csv")
```

## Exercises

### Exercise 1


There are 26 variables and 935 rows. Each row is a person (so in theory there are 934 people in the nobel dataset).

```{r get info on dataset}

glimpse(nobel)
#head(nobel) - gives it looking more like a table

nobel_living <- nobel %>%
  filter(country != "NA" & gender != "org" & died_date == "NA")


```

### Exercise 2

Remove this text, and add your answer for Exercise 1 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 3

Remove this text, and add your answer for Exercise 1 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 4

...

### Exercise 5

...

### Exercise 6

...
