---
title: "Lab 03 - Nobel laureates"
author: "Benjamin Egan"
date: "Started on 1/27"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
nobel <- read_csv("data/nobel.csv")
```

## Exercises

### Exercise 1

Using dataset "Nobel", which examines information about nobel winners
There are 26 variables and 935 rows. Each row is a person (so in theory there are 934 people in the nobel dataset).

```{r get info on dataset}

glimpse(nobel)
#count(nobel) can give a table that tells me the number in each variable
#head(nobel) - gives it looking more like a table

```

### Exercise 2

filtered out people who don't have a country, organizations that won a nobel, and people who are dead
``` {r filtered nobel}

nobel_living <- nobel %>%
 filter(country != "NA" & gender != "org" & is.na(died_date))

```


### Exercise 3

Created a dataset for American winners in physics, medicine, chemistry, and economics
``` {r Are they in the US?}
#are they in the US
nobel_living <- nobel_living %>%
  mutate(
    country_us = if_else(country == "USA", "USA", "Other")
  )

#Physics, Medicine, Chemistry, and Economics
nobel_living_science <- nobel_living %>%
  filter(category %in% c("Physics", "Medicine", "Chemistry", "Economics"))

```

Graph for the relationship between the category of prize and whether the laureate was in the US when they won the nobel prize
```{r visual plot}

ggplot(
  data = nobel_living_science,
  mapping = aes(
    x = country_us,
  )
) +
  facet_wrap(~category)+
  theme_bw()+
  geom_bar()+
  coord_flip()+
  labs(
      x = "Country",
      y = "Number of Prize Winners",
      title = "Relationship Between Prize Winner and Country"
  )
 
```
More USA winners in each category. Economics has a disproportionate number of USA winners.


### Exercise 4

...

### Exercise 5

...

### Exercise 6

...
